A Polls-of-Polls Forecast for the 2024 United States Presidential Election Through Generalized Linear Model

### 2024-11-04 paper/paper.qmd
fix error: Error in parse()

library(tidyverse)
library(here)
library(kableExtra)
library(broom.mixed)
library(knitr)
library(kable)
library(rstanarm)

@@

# Display the summary statistics in a nicely formatted table
summary_stats |>
  kable
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)

>>>>

library(tidyverse)
library(here)
library(kableExtra)
library(broom.mixed)
library(knitr)
library(rstanarm)

@@

# Display the summary statistics in a nicely formatted table
summary_stats %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
